\name: A hierarchical Bayesian model for Supernova Cosmology

### 2018-03-19 papers/methods/paper.tex
Paper update with lowz citations

Sitting comfortably between the traditional models simplicity and the complexity of forward modelling lies hierarchical Bayesian Models. With the introduction of multiple layers in our model, we can add far more flexibility than a traditional analysis whilst still maintaining most of the computational benefits that come from having a tractable likelihood. \citet{Mandel2009}, \citet{Mandel2011} and \citet{Mandel2017} construct a hierarchical model that they apply to supernova light curve fitting. \citet{March2011} derive a hierarchical model and simplify it by analytically marginalising over nuisance parameters to provide increased flexibility with reduced uncertainty over the traditional method, but does not incorporate bias correction. \citet{March2014, Karpenka2015} improve upon this by incorporating redshift-dependent magnitude corrections from \citet{Perrett2010} to remove bias, and validate on 100 realisations of SNLS like simulations. The recent BAHAMAS model \citep{Shariff2016} builds on this and reanalyses the JLA dataset (using their redshift dependent bias corrections), whilst including extra freedom in the correction factors $\alpha$ and $\beta$, finding evidence for redshift dependence on $\beta$. \citet{Ma2016} performed a reanalysis of the JLA dataset within a Bayesian formulation, finding significant differences in $\alpha$ and $\beta$ values from the original analysis from \citet{Betoule2014}. Notably, these methods rely on data that is bias corrected or ignore biases, however the UNITY framework given by \citet{Rubin2015} incorporates selection efficiency analytically in the model, and is applied to the Union 2.1 dataset \citep{Suzuki2012}. The simplification made by the UNITY analysis is that the bias is well described by an analytic function, and this function is fixed such that selection effects are assumed to be determined with perfect precision. Their model was validated on thirty realisations of statistics.

@@

Simulations (using the SNANA package) follow the observational schedule and observing conditions for the DES and LowZ surveys. In addition to the improvements in the scatter models over the simple data, we also include peculiar velocities for the LowZ sample, and our full treatment of systematics. Our simulated populations are sourced from \citet[][hereafter {\sk}]{Scolnic2016}. The selection effects were quantified by comparing all the generated supernovae to those that pass our simulated cuts, as shown in Figure~\ref{fig:sf_snana}. It is from this simulation that our analytic determination of the selection functions for the LowZ and DES survey are based. We note that there was no significant difference in the selection effect of Malmquist bias between using the {\gten} or {\celeven} scatter model compared to the fit uncertainty.

>>>>

Sitting comfortably between the traditional models simplicity and the complexity of forward modelling lies hierarchical Bayesian Models. With the introduction of multiple layers in our model, we can add far more flexibility than a traditional analysis whilst still maintaining most of the computational benefits that come from having a tractable likelihood. \citet{Mandel2009}, \citet{Mandel2011a} and \citet{Mandel2017} construct a hierarchical model that they apply to supernova light curve fitting. \citet{March2011} derive a hierarchical model and simplify it by analytically marginalising over nuisance parameters to provide increased flexibility with reduced uncertainty over the traditional method, but does not incorporate bias correction. \citet{March2014, Karpenka2015} improve upon this by incorporating redshift-dependent magnitude corrections from \citet{Perrett2010} to remove bias, and validate on 100 realisations of SNLS like simulations. The recent BAHAMAS model \citep{Shariff2016} builds on this and reanalyses the JLA dataset (using their redshift dependent bias corrections), whilst including extra freedom in the correction factors $\alpha$ and $\beta$, finding evidence for redshift dependence on $\beta$. \citet{Ma2016} performed a reanalysis of the JLA dataset within a Bayesian formulation, finding significant differences in $\alpha$ and $\beta$ values from the original analysis from \citet{Betoule2014}. Notably, these methods rely on data that is bias corrected or ignore biases, however the UNITY framework given by \citet{Rubin2015} incorporates selection efficiency analytically in the model, and is applied to the Union 2.1 dataset \citep{Suzuki2012}. The simplification made by the UNITY analysis is that the bias is well described by an analytic function, and this function is fixed such that selection effects are assumed to be determined with perfect precision. Their model was validated on thirty realisations of statistics.

@@

Simulations (using the SNANA package) follow the observational schedule and observing conditions for the DES and LowZ surveys, where the LowZ sample is comprised of CfA3 \citep{Hicken2009, Hicken2009a}, CfA4 \citep{Hicken2012} and CSP \citep{Contreras2010,Folatelli2010,Stritzinger2011}.

 In addition to the improvements in the scatter models over the simple data, we also include peculiar velocities for the LowZ sample, and our full treatment of systematics. Our simulated populations are sourced from \citet[][hereafter {\sk}]{Scolnic2016}. The selection effects were quantified by comparing all the generated supernovae to those that pass our simulated cuts, as shown in Figure~\ref{fig:sf_snana}. It is from this simulation that our analytic determination of the selection functions for the LowZ and DES survey are based. We note that there was no significant difference in the selection effect of Malmquist bias between using the {\gten} or {\celeven} scatter model compared to the fit uncertainty.
